Enhancement of SDR in Thessaloniki

### 2024-09-05 GHI_enh_03_process.tex
Commit 2024-09-05 23:10

@@

\usepackage{bookmark}
\urlstyle{same}

@@

\subsection{Time series decomposition tests}\label{time-series-decomposition-tests}

@@

\begin{verbatim}
2024-09-05 08:08:34.0 athan@sagan GHI_enh_03_process.R 5.165189 mins
\end{verbatim}

>>>>

\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\urlstyle{same} % disable monospaced font for URLs

@@

@@

\hypertarget{time-series-decomposition-tests}{%
\subsection{Time series decomposition tests}\label{time-series-decomposition-tests}}

@@

\begin{verbatim}
2024-09-05 19:30:15.8 athan@sagan GHI_enh_03_process.R 3.894151 mins
\end{verbatim}
